Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
chore: minor on paragraph

\paragraph{Centralized Actor-Critic Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
leveraging centralized information during training to learn decentralized policies for execution. 
This approach addresses the challenges of partial observability and non-stationarity while maintaining the scalability of decentralized execution. % 
Actor-critic methods are well-suited for the CTDE paradigm, 
where a centralized critic provides feedback to decentralized actors~\cite{DBLP:conf/icml/RashidSWFFW18,DBLP:journals/corr/SunehagLGCZJLSL17,yu2022surprising,DBLP:conf/nips/LoweWTHAM17}. 
% 
The most influential algorithms in this area are the one called policy-based methods (i.e., the ones that learn a policy directly).
%
Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates. 
Each agent then learns a deterministic policy based on its local observations. % 
Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
Another class of algorithms, called value-based methods, learn a value function that estimates the expected return for each agent.
%
Value Decomposition Networks (VDN)~\cite{DBLP:journals/corr/SunehagLGCZJLSL17} and QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} are representative algorithms in this category. 
VDN factorizes the joint Q-function into a sum of individual agent Q-functions, simplifying the learning process. 
QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
allowing for more complex representations of joint action values. %

>>>>

\paragraph{Centralized Training Methods} CTDE is a prominent paradigm in MARL~\cite{ning2024survey}, 
leveraging centralized information during training to learn decentralized policies for execution. 
This approach addresses the challenges of partial observability and non-stationarity while maintaining the scalability of decentralized execution. % 
Actor-critic methods are well-suited for the CTDE paradigm, 
where a centralized critic provides feedback to decentralized actors~\cite{DBLP:conf/icml/RashidSWFFW18,DBLP:journals/corr/SunehagLGCZJLSL17,yu2022surprising,DBLP:conf/nips/LoweWTHAM17}. 
% 
The most influential algorithms in this area are the one called policy-based methods (i.e., the ones that learn a policy directly).
%
Multi-agent deep deterministic policy Gradient (MADDPG)~\cite{DBLP:conf/nips/LoweWTHAM17} employs a centralized critic that has access to the states and actions of all agents, providing more informative feedback for policy updates. 
Each agent then learns a deterministic policy based on its local observations. % 
Building on the actor-critic framework, Multi-Agent Proximal Policy Optimization (MAPPO)~\cite{yu2022surprising} extends the centralized critic concept to the policy optimization setting. 
MAPPO leverages a centralized critic to estimate advantage functions for policy updates, while individual agents learn stochastic policies. 
This approach has shown promising results in various cooperative and competitive MARL tasks, exhibiting improved sample efficiency and robustness compared to MADDPG. % 
Another class of algorithms, called value-based methods, learn a value function that estimates the expected return for each agent.
%
Value Decomposition Networks (VDN)~\cite{DBLP:journals/corr/SunehagLGCZJLSL17} and QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} are representative algorithms in this category. 
VDN factorizes the joint Q-function into a sum of individual agent Q-functions, simplifying the learning process. 
QMIX improves upon VDN by learning a monotonic mixing function that combines individual Q-values, 
allowing for more complex representations of joint action values. %
